\documentclass[%
  reprint,
  aps,
  pra,
  superscriptaddress,
  a4paper,
]{revtex4-2}


\usepackage{authororcid}


% For draft stage
\usepackage{lipsum}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[
  bookmarks=false,
  bookmarks=true,
  colorlinks,
  linkcolor=blue,
  urlcolor=blue,
  citecolor=blue,
  plainpages=false,
  pdfpagelabels,
  final,
  breaklinks=true
]{hyperref}
\hypersetup{
pdftitle={The Author ORCID package}, 
pdfauthor={Emilio Pisanty}
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



\begin{document}



\title{The Author ORCID package}

\author{Emilio Pisanty}
\orcid{0000-0003-0598-8524}
\email{emilio.pisanty@mbi-berlin.de}
\affiliation{Max Born Institute for Nonlinear Optics and Short Pulse Spectroscopy, Max Born Strasse 2a, D-12489 Berlin, Germany}

\author{Josiah Carberry}
\orcid{0000-0002-1825-0097}
\affiliation{Department of Psychoceramics, Brown University}

\date{\today}

\begin{abstract}
The Author ORCID package is a {\LaTeX} package for the REVTeX class, which handles ORCID iD attribution for authors.
\end{abstract}

\maketitle




This package adds support for ORCID iDs to the REVTeX class. It provides the following features:

\begin{itemize}
\item
An \verb|\orcidlogo{width}| command, which produces the ORCID logo at the specified width: small, \orcidlogo{8pt}, or bigger:

\orcidlogo{20pt}

This graphic is produced within \texttt{tikz}, and it is a transcription of the SVG version.

\item
An \verb|\orcid{orcid-id}| command, which can be added after each \verb|\author| with the corresponding numerical iD. 
An example usage is as follows:
\begin{verbatim}
\author{Josiah Carberry}
\orcid{0000-0002-1825-0097}
\affiliation{Department of Psychoceramics, 
               Brown University}
\end{verbatim}
This will produce ORCID badges after each author for which an iD has been specified, hyperlinked to that author's ORCID record.


\item
An \verb|\listoforcidids| command, which produces an unnumbered section listing all the author ORCID iDs, suitably hyperlinked, as shown below.

\end{itemize}

This package calls on the \texttt{tikz}, \texttt{xcolor} and \texttt{enumitem} packages as dependences.

To be honest, the code here is quite `hacky' and probably quite fragile.
It is unlikely that this is a sustainable way forward, but the code presented here will hopefully be a useful prototype and temporary fix until full ORCID iD support is included into the REVTeX class itself.

For full clarity, Josiah Carberry is a fictional person and has no involvement with this work---the authorship is wholly mine (E.\ Pisanty), and Carberry (described as an expert in the study of `cracked pots' by Wikipedia) is \href{https://support.orcid.org/hc/en-us/articles/360006897674-Structure-of-the-ORCID-Identifier}{listed by ORCID} as a suitable example author for demonstration purposes.

\listoforcidids



\end{document}













